When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-07 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added refs to supplementary material

Our hypotheses were derived from the results of Westbrook et al.[-@Westbrook2013].
As a manipulation check, we hypothesized that with increasing $n$-back level the (1a) the signal detection parameter $d'$ declines, while (1b) reaction time and (1c) perceived task load increase.
Regarding the associations of task load and effort discounting we hypothesized that (2a) SVs decline with increasing $n$-back level, and (2b) they do so even after controlling for declining task performance.
And finally, we hypothesized that the CAD paradigm can show inter-individual differences in effort discounting, such that participants with higher NFC have (3a) lower SVs for 1-back but higher SVs for 2- and 3-back, (3b) lower perceived task load across all levels, and (3c) higher aversion against 1-back but lower aversion against 2- and 3-back.
Each hypothesis is detailed in the [Design Table](#DesignTableSection) in the Appendix.

@@

All NASA-TLX subscale scores increased across $n$-back levels.
The effort subscale (`r apa_print(hypothesis1c_effort_rmanova)$full_result$level`, `r apa_print(hypothesis1c_effort_BF)$statistic`) increased across all levels, but the magnitude of change decreased from 1- to 2-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X1_X2`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE, paired = TRUE))$statistic`) to 3- to 4-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
Three subscales had significant differences between all contrasts except for 3- versus 4-back:
While ratings on the frustration and time subscales were higher for more difficult levels (`r apa_print(hypothesis1c_frustration_rmanova)$full_result$level`, `r apa_print(hypothesis1c_frustration_BF)$statistic`, and `r apa_print(hypothesis1c_time_rmanova)$full_result$level`, `r apa_print(hypothesis1c_time_BF)$statistic`, respectively), ratings on the performance subscale decreased with higher $n$ (`r apa_print(hypothesis1c_performance_rmanova)$full_result$level`, `r apa_print(hypothesis1c_performance_BF)$statistic`).
Ratings on the mental subscale consistently increased across all levels (`r apa_print(hypothesis1c_mental_rmanova)$full_result$level`, `r apa_print(hypothesis1c_mental_BF)$statistic`).
Ratings on the physical subscale were higher for more difficult levels (`r apa_print(hypothesis1c_physical_rmanova)$full_result$level`, `r apa_print(hypothesis1c_physical_BF)$statistic`), apart from the contrasts 2- versus 3-back (`r apa_print(pairs(hypothesis1c_physical_emm))$statistic$X2_X3`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE, paired = TRUE))$statistic`) and 3- versus 4-back (`r apa_print(pairs(hypothesis1c_physical_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 3], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).

@@

When asking participants what motivated their decisions in the effort discounting, `r format(round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid boredom, `r format(round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted a challenge, `r format(round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid effort, and `r format(round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to relax.
The remaining `r format(round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
**Figure XX in the Supplement** shows the different motivations in the context of the SVs per $n$-back level.

@@

```{r H2b-results, echo=FALSE, message=FALSE, warning=FALSE}
kable(h2b_result.table,
        caption = "Results of the multi level model on the influence of n-back level (as a declining logistic contrast) and task performance on subjective values.",
        booktabs = T,                          # no vertical lines
        escape = F,                            # correctly print special characters)
        align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
    footnote(general = "$SE$ = standard error, $df$ = degrees of freedom, $SD$ = standard deviation.",
             escape = F,                    # correctly print special characters
             threeparttable = T)            # line breaks in the footnote
```

@@

With another rmANOVA we investigated whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the $n$-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction (`r apa_print(hypothesis3c_model)$full_result$nfcmedian_nlevels`).
Post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`) (right panel of Figure\ \@ref(fig:h3ac-plot)).
Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), but again, there were large inter-individual differences.

>>>>

Our hypotheses were derived from the results of Westbrook et al.[-@Westbrook2013].
As a manipulation check, we hypothesized that with increasing $n$-back level the (1a) the signal detection parameter $d'$ declines, while (1b) reaction time and (1c) perceived task load increase.
Regarding the associations of task load and effort discounting we hypothesized that (2a) SVs decline with increasing $n$-back level, and (2b) they do so even after controlling for declining task performance.
And finally, we hypothesized that the CAD paradigm can show inter-individual differences in effort discounting, such that participants with higher NFC have (3a) lower SVs for 1-back but higher SVs for 2- and 3-back, (3b) lower perceived task load across all levels, and (3c) higher aversion against 1-back but lower aversion against 2- and 3-back.
Each hypothesis is detailed in the Design Table in the Supplementary Material.

@@

All NASA-TLX subscale scores increased across $n$-back levels.
The effort subscale (`r apa_print(hypothesis1c_effort_rmanova)$full_result$level`, `r apa_print(hypothesis1c_effort_BF)$statistic`) increased across all levels, but the magnitude of change decreased from 1- to 2-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X1_X2`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE, paired = TRUE))$statistic`) to 3- to 4-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
Three subscales had significant differences between all contrasts except for 3- versus 4-back:
While ratings on the frustration and time subscales were higher for more difficult levels (`r apa_print(hypothesis1c_frustration_rmanova)$full_result$level`, `r apa_print(hypothesis1c_frustration_BF)$statistic`, and `r apa_print(hypothesis1c_time_rmanova)$full_result$level`, `r apa_print(hypothesis1c_time_BF)$statistic`, respectively), ratings on the performance subscale decreased with higher $n$ (`r apa_print(hypothesis1c_performance_rmanova)$full_result$level`, `r apa_print(hypothesis1c_performance_BF)$statistic`).
Ratings on the mental subscale consistently increased across all levels (`r apa_print(hypothesis1c_mental_rmanova)$full_result$level`, `r apa_print(hypothesis1c_mental_BF)$statistic`).
Ratings on the physical subscale were higher for more difficult levels (`r apa_print(hypothesis1c_physical_rmanova)$full_result$level`, `r apa_print(hypothesis1c_physical_BF)$statistic`), apart from the contrasts 2- versus 3-back (`r apa_print(pairs(hypothesis1c_physical_emm))$statistic$X2_X3`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE, paired = TRUE))$statistic`) and 3- versus 4-back (`r apa_print(pairs(hypothesis1c_physical_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 3], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
The full results of these manipulation checks are listed in Table S.1 to S.8 in the Supplementary Material.

@@

When asking participants what motivated their decisions in the effort discounting, `r format(round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid boredom, `r format(round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted a challenge, `r format(round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid effort, and `r format(round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to relax.
The remaining `r format(round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
Figure S.1 in the Supplementary Material shows the different motivations in the context of the SVs per $n$-back level.

@@

```{r H2b-results, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(h2b_result.table,
        caption = "Results of the multi level model on the influence of n-back level (as a declining logistic contrast) and task performance on subjective values.",
        escape = FALSE,
        note = "$SE$ = standard error, $df$ = degrees of freedom, $SD$ = standard deviation.",
        placement = "H")
```

@@

With another rmANOVA we investigated whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the $n$-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction (`r apa_print(hypothesis3c_model)$full_result$nfcmedian_nlevels`).
Post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`) (right panel of Figure\ \@ref(fig:h3ac-plot)).
Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), but again, there were large inter-individual differences.
The full results of these analyses of NFC group differences can be found in Table S.11 to S.15 in the Supplementary Material.
